Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-17 talk/iwtc11/paper.tex
clairify

\begin{abstract}
By introducing loop peeling into the optimization step of a tracing
jit, the effect of optimizations already in place will be increased
greatly. Not only will they become able to move loop invariant code
out of loop. They will also become able to reuse results from the
previous iteration. Also, the implementation of excising optimizations
can be left almost intact as they will not have to interact much with
the loop peeling.

Several benchmarks executed on the PyPy python JIT show over 2
times increase in speed when loop peeling was introduced. This makes
some of them almost match optimized C performance and become over XXX
times faster than cpython.
\end{abstract}

>>>>

\begin{abstract}
By introducing loop peeling into the optimization step of a tracing
jit the effect of optimizations already in place will be increased
greatly. Not only will they become able to move loop invariant code
out of loop. They will also become able to reuse results from the
previous iteration. Also, the implementation of excising optimizations
can be left almost intact as they will not have to interact much with
the loop peeling.

Several benchmarks, with few guard failures, executed on the
PyPy python JIT show over 2 
times increase in speed when loop peeling was introduced. This makes
some of them almost match optimized C performance and become over XXX
times faster than cpython.
\end{abstract}
